---
title: "HW 01 (?) - Airbnb listings in Edinburgh"
author: "Gerrit"
date: "started 2023-01-19, currently `r Sys.Date()`"
output: github_document
---

## Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(dsbox)
```

## Exercises

### Exercise 1

there are `r nrow(edibnb)` entries in the data set.

### Exercise 2

each row represesnts a different AirBNB in Edinurgh.

### Exercise 3

facet wrapped to 4 rows, since it seemed to make the graphs large enough to be visible, and filtered to prices < 500, so that the bulk of the data is actually large enough to compare.

```{r prices-neighbourhoods}
ggplot(data = edibnb %>% filter(price < 300), mapping = aes(x = price))+
  geom_histogram(stat = "bin", binwidth = 20)+
  facet_wrap(~neighbourhood, nrow = 4)
```

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

bechdel90_13 %>%
  group_by(binary) %>%
  summarise(
    med_budget = median(budget_2013),
    med_domgross = median(domgross_2013, na.rm = TRUE),
    med_intgross = median(intgross_2013, na.rm = TRUE)
    )

```{r top-5-median}
#edibnb %>%
#  group_by(edibnb$neighbourhood) %>%
#    med_price = median(edibnb$price, na.rm = TRUE) %>%
#    arrange(edibnb$neighbourhood, n)%>%
#    slice_max(n, n=5)

edibnb %>%
  filter(!is.na(price))%>%
  group_by(neighbourhood) %>%
  summarise(med_price = median(price)) %>%
  top_n(n = 5, med_price) %>%
  arrange(desc(med_price)) %>%
  print()
```

```{r top-5-median-plot}
# remove this comment and add the code for Exercise 4 here
```

```{r top-5-median-summary-stats}
# remove this comment and add the code for Exercise 4 here
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r review-scores-rating}
# remove this comment and add the code for Exercise 5 here
```