---
title: "Visualizing Starwars characters"
author: "Mine Çetinkaya-Rundel"
format: html
editor: visual
---

```{r}
#| label: load-packages
#| include: false

library(tidyverse)
```

1.  Glimpse at the starwars data frame.

```{r}
#| label: glimpse-starwars

glimpse(starwars)
```

2.  Modify the following plot to change the color of all points to `"pink"`.

```{r}
#| label: scatterplot

ggplot(starwars, 
       aes(x = height, y = mass, color = gender, size = birth_year)) +
  geom_point(color = "pink")
```

3.  Add labels for title, x and y axes, and size of points. Uncomment to see the effect.

```{r}
#| label: scatterplot-labels

ggplot(starwars, 
       aes(x = height, y = mass, color = gender, size = birth_year)) +
  geom_point(color = "#30509C") +
  labs(
    title = "Mass vs Height",
    x = "Character Height", 
    y = "Character Mass",
    size = "Birth Year"
    )
```

4.  Pick a single numerical variable and make a histogram of it. Select a reasonable binwidth for it.

(A little bit of starter code is provided below, and the code chunk is set to not be evaluated with `eval: false` because the current code in there is not valid code and hence the document wouldn't knit. Once you replace the code with valid code, set the chunk option to `eval: true`, or remove the `eval` option altogether since it's set to `true` by default.)

```{r}
#| label: histogram
#| eval: true

ggplot(starwars, aes(x = -birth_year, y =)) +
  geom_histogram(stat = "bin", binwidth = 10)
```

5.  Pick a numerical variable and a categorical variable and make a visualization (you pick the type!) to visualization the relationship between the two variables. Along with your code and output, provide an interpretation of the visualization.

```{r}
#| label: num-cat

#Jabba is a really annoying outlier that makes it hard to see anything else on the graph with much detail, so this is a little filter to drastically improve this dataset in every single way

starwarsnojabba <- starwars%>%
  filter(name != "Jabba Desilijic Tiure")

#I wanted to see what a jitter plot does, turns out its just a point plot, but with a little bit of randomness added, so that for very dense data, the points are slightly more spread out

ggplot(data = starwarsnojabba, mapping = aes(x = mass, y = height, color = sex)) + 
  geom_jitter()

       

```

from this graph, we can see that:

A) there are way more males than females in this data set

B) There is a fairly linear connection between height and mass, as one increase, so does the other, unsurprisingly.

C) Males have a broader range, with the cluster of the shortest and lightest characters being almost exclusively male. The tallest and heaviest are also males. 

E) Withing the main cluster of characters, we can see that males are pretty much all heavier than the female characters, but that they aren't that much taller.

6.  Pick a single categorical variable from the data set and make a bar plot of its distribution.

```{r}
#| label: barplot

#bar plot for eye color of the characters

ggplot(data = starwarsnojabba, mapping = aes(x = eye_color))+
  geom_bar()

```

7.  Pick two categorical variables and make a visualization to visualize the relationship between the two variables. Along with your code and output, provide an interpretation of the visualization.

```{r}
#| label: cat-cat

ggplot(data = starwars, mapping = aes(color = sex, y = homeworld)) +
  geom_bar()

```

so basically, there are way more males than females in this data set.  

8.  Pick two numerical variables and two categorical variables and make a visualization that incorporates all of them and provide an interpretation with your answer.

(This time no starter code is provided, you're on your own!)

```{r}
#| label: multi

```

Interpretation goes here...