---
title: "NYC Flights"
author: "Gerrit Blauvelt"
date: "`r Sys.Date()`"
output: html_document
---
excercises to address:
5.2.4
5.3.1
5.4.1
5.5.2
5.6.7
5.7.1


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(nycflights13)

```


5.2.4

``` {r}
#All flights that arrived 2 or more hours late
filter(flights, arr_delay >=120)

#All flights going to Houston, TX (George Bush Intercontinental & William P. Hobby Airports)
filter(flights, dest == "IAH" | dest == "HOU")

#All flights flown by United, American, or Delta
filter(flights, carrier %in% c("UA","AA","DL"))

#All flights that departed in "Summer" (July, August, September)
filter(flights, month %in% c(7, 8, 9))

#Flights which departed on time, but arrive 2 or more hours late
filter(flights, dep_delay <= 0 & arr_delay >= 120)

#Flights which departed at least 1 hour late, but made up at least 30 minutes in the air
filter(flights, dep_delay >= 60 & arr_delay <= (dep_delay - 30) )

#Flights which departed from 12am to 6am (I don't like this dataset, it goes 23:59 -> 24:00 -> 00:01. It should go 23:59 -> 00:00 -> 00:01)
filter(flights, dep_time <= 600)



```



Another useful dplyr filtering helper is between(). What does it do? Can you use it to simplify the code needed to answer the previous challenges?

between() checks if a value is between an upper and lower bound. It might be useable for the summer months, and, If I did the midnight to 6am departure differently (if the lowest bound wasn't just 0 already), it would be useful there.


How many flights have a missing dep_time? What other variables are missing? What might these rows represent?

there are `r nrow(filter(flights,is.na(dep_time)))` without a departure time



Why is `NA ^ 0` not missing? Why is `NA | TRUE` not missing? Why is `FALSE & NA` not missing? Can you figure out the general rule? (`NA * 0` is a tricky counterexample!)

NA^0 is 1, because anything raised to 0 is 1. For the rest of them I don't entirely understand


**5.3.1**

```{r}
#arranged so that flights with NA values are at the top, with the idea that if a flight is going to have any missing values, it will at the very least have a missing arrival time. It could have everything except a missing arrival time (best case scenario it departed and then turned around). For any other variable, there could be an actual value, but there might still be an NA in arr_time that wouldn't get caught sorting by say tail number. 
arrange(flights, desc(is.na(arr_time)), arr_time)

#arranged by flights that departed the earliest relative to their scheduled time
arrange(flights, dep_delay)

#arranged by flights that have the highest speed (distance/time (miles/minute)), descending order, so that fastest speed is at the top
arrange(flights, desc(distance/air_time))

#arranged by flights the traveled the farthest
arrange(flights, desc(distance))

#arranged by flights that traveled the shortest
arrange(flights, distance)

```